---
title: "Lab 01 - Hello R"
author: "melissa maffeo"
date: "jan 15 2026"
output: 
  html_document: 
    fig_height: 4
    fig_width: 9
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
data("datasaurus_dozen")
```

## Exercises

### Exercise 1

Melissa doesn't know the answer to E1! Am I doing this right? I have no idea. 

### Exercise 2

Here is a visual representation of the dino dataset: 

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Next, let's calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
I'm not sure what you're looking for here. Do you want to interpret the correlation? The correlation is -.064. 


### Exercise 3

Here's another dataset. This one is shaped like a star. 

```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Clunky star. 

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
I noticed that there's a relationship of -.062. Weak negative?  


### Exercise 4

Add your code and narrative to complete this exercise. Use the conventions from the previous exercises to name your chunks and organize your work.

```{r plot-star, fig.height=10, fig.width=5}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r}

```

### Exercise 5

This is your final exercise! Add code and narrative as needed. Be creative and show off what you’ve learned so far.
Add code and narrative as needed.

To add additional R chunks, you can either type the backticks, curly braces, and the letter `r`, or use the "Insert Chunk" button above (the green C+ icon). Have fun!


